\documentclass{ali-resume}

\author{Alistair Pattison}
\title{
{\it (651) 706-6713}
\ | \
{\it pattisona@carleton.edu}
\ | \
\href{http://alipatti.com}{\it alipatti.com}
}

\addbibresource{publications.bib}

\begin{document}

\maketitle

\section{Education}

\resumeitem{Bachelors of Arts, Mathematics \& Statistics}
{Carleton College}
{September 2020 -- June 2024}

\begin{itemize}
	\item 3.99 GPA, Dean's List every possible term.
	\item Captain of varsity track and field, three-time MIAC conference finalist, two-time all-conference honorable mention.
	\item Studied abroad at the University of Cambridge taking classes in cryptography, WWII history, and the history of computing.
\end{itemize}

\resumeitem{Talented Youth Mathematics Program}
{University of Minnesota}
{2015 -- 2020}

\begin{itemize}
	\item Completed selective high-school math program culminating in six semesters of set theory, vector calculus, linear algebra, and differential equations.
\end{itemize}

\section{Work Experience}

% \resumeitem{Statistical Consultant}{Some nonprofit group}{September 2023 -- present}

% \begin{itemize}
% 	\item TODO
% \end{itemize}

\resumeitem{Research Assistant}
{University of Minnesota}
{September 2022 -- August 2023}

\begin{itemize}
	\item Researched and developed a method for reporting abuse and misinformation on encrypted messaging platforms (e.g. WhatsApp or Signal) that provably maintains users' anonymity and privacy.
	\item Presented findings at a leading security conference and gave talks at weekly lab seminars.
	\item Wrote a proof-of-concept \href{http://github.com/alipatti/cerberus}{implementation of the protocol in Rust}.
\end{itemize}

\resumeitem{Teaching Assistant}
{Carleton College}
{March 2021 -- present}

\begin{itemize}
	\item Tutor students, grade homework, and hold office hours for classes in the math and computer science departments.
	% \item Work closely with the professor to establish clear grading guidelines and adjust curriculum to better serve students.
	\item Classes include
	      real analysis, % (MATH 321),
	      abstract algebra, % (MATH 342),
	      data visualization, % (CS 314),
	      artificial intelligence, % (CS 321),
	      algorithms, % (CS 252),
	      and math structures, % (MATH 236),
	      %   and calculus. % (MATH 120).
\end{itemize}

\resumeitem{The Food Guy}
{YMCA Camp Widjiwagan}
{June -- September 2021}

\begin{itemize}
	\item Individually managed the purchase and distribution of food for nearly 200 wilderness trips across the US and Canada.
	\item Oversaw a \$95,000 budget alongside two other employees and taught basic nutrition to kids aged 12 to 18.
	\item Lead a week-long canoeing trip with BOLD, a program dedicated to making the outdoors more diverse and accessible.
\end{itemize}

\resumeitem{Dining Hall Worker}
{Carleton College}
{September 2020 -- March 2021}

\resumeitem{Farm Hand}
{Hansen Christmas Tree Farm}
{2018 -- 2021}

\resumeitem{Owner}
{Pattison Lawn Care}
{2015 -- 2020}

\null

\section{Publications}

% TODO add url: (will appear at https://arxiv.org/user/)
\fullcite{cerberus}

\section{Awards}

\textit{Phi Beta Kappa} -- One of nine Carleton juniors inducted into national honors society on the basis of academic merit.

\textit{National Merit Scholarship} -- Competitive scholarship provides four years of partial financial support for undergraduate study.

\textit{James F. Koehler Scholarship} -- Endowed scholarship given to a Carleton math major.

\section{Projects}

\newcommand{\project}[2]{%
	\subsection{#1
		\hfill
		\normalfont \small \faicon{github}
		\href{http://github.com/alipatti/#2}{\textit{alipatti/#2}}
	}}

\project{Ole or Carl?}{oleorcarl}

\begin{itemize}
	\item This project tests the validity of a long-standing stereotype that students from Northfield's two colleges look meaningfully different. If they are, then a machine learning model should be able to tell them apart? Right?
	\item Uses an SVM classifier on embeddings of student's faces taken from directory photos.
\end{itemize}

\project{Carleton Course Classifier}{course-classifier}

\begin{itemize}
	\item A Tensorflow language model that predicts the department and course number given a course description.
	\item Achieves 64\% accuracy in a 54-class problem using a neural net and deep word embeddings.
\end{itemize}

\section{Skills}

\textbf{Programming:}
Python (numpy, pandas, tensorflow, sklearn, matplotlib), R (tidyverse, ggplot2), JavaScript (TypeScript, React, Next.js, d3.js), \LaTeX, Rust, Java, SQL, git, Docker.

\end{document}
